Preparación de datos

### 2022-05-24 production/prod_prep.Rmd
ajustes bbdd
- individual y comunal

#Impute midpoint of income ranges
elsoc_long_2016_2021$m30_rec <-
as.numeric(car::recode(elsoc_long_2016_2021$m30,
           "1=110000;2=251000;3=305000;4=355000;5=400000;
            6=445000;7=490000;8=535000;9=585000;10=640000;11=700000;12=765000;
            13=845000;14=935000;15=1040000;16=1180000;17=1375000;18=1670000;
            19=2275000;20=2700000;NA=NA;c(-888,-999)=NA"))
#Recode DK/DA of Income to NA
elsoc_long_2016_2021$m29_rec <-
  as.numeric(car::recode(elsoc_long_2016_2021$m29,"c(-888,-999)=NA"))

#replace NA of income with new imputed variable
elsoc_long_2016_2021$m29_imp <- 
  ifelse(test = !is.na(elsoc_long_2016_2021$m29_rec),
         yes =  elsoc_long_2016_2021$m29_rec,
         no =  elsoc_long_2016_2021$m30_rec)

@@

# N Household:
elsoc_long_2016_2021 <-
  elsoc_long_2016_2021 %>%
  mutate(n_hogar =
           dplyr::case_when(ola == 1 ~ nhogar1,
                            ola == 2 ~ m46_nhogar,
                            ola == 3 ~ m54,
                            ola == 4 ~ m54))
sjmisc::frq(elsoc_long_2016_2021$n_hogar)

@@

elsoc_long_2016_2021$quintil <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$quintil,
                      label = "Houshold income quintile per capita")

@@

elsoc_long_2016_2021$quintil1 <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$quintil1,
                      label = "Houshold income quintile per capita (NA)") 
sjmisc::frq(elsoc_long_2016_2021$quintil1)
#Age Ranges
elsoc_long_2016_2021$edad <- 
  factor(car::recode(elsoc_long_2016_2021$m0_edad, 
                     "18:29=1;30:49=2;50:64=3;65:150=4"),
         labels = c('18-29', '30-49', '50-64', '65 or more'))
elsoc_long_2016_2021$edad <-
  sjlabelled::set_label(elsoc_long_2016_2021$edad, 
                        label = c("Age groups")) 
# Other controls______________________________________________________________
# Subjective social status: individual ____________________________

@@

elsoc_long_2016_2021$know_inm <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$know_inm, 
                      label = "Known: Immigrants") 
elsoc_long_2016_2021$know_inm <-
sjlabelled::set_labels(x = elsoc_long_2016_2021$know_inm,
                       labels = c("None","Few","Some","Quite a few","Many"))

@@

# Select data______________________________________________________________

df_study1 <- 
elsoc_long_2016_2021 %>% 
  select(idencuesta,ola,region,region_cod,comuna,comuna_cod,
         starts_with("in_"),
         educ,educ_n,ing_pc,quintil,quintil1,
         ess,ess_inm,
         nation,know_inm,pos_id,edad)

@@

# save data
save(df_study1,file = here::here("input/data-proc/study_1.RData"))

# save codebook
sjPlot::view_df(df_study1,
        show.frq = T, 
        show.prc = T, 
        show.na = T,
        file = here::here("output/df_study1.html"))
```

@@

load(file = here::here("input/data-proc/study_1.RData"))
load(file = here::here("input/data-proc/study_1_comunas.RData"))

@@

# save data____________________________________________________________________
save(df_study1_ind_comunas,file = here::here("input/data-proc/df_study1_ind_comunas.RData"))

# save codebook
sjPlot::view_df(df_study1_ind_comunas,
        show.frq = T, 
        show.prc = T, 
        show.na = T,
        file = here::here("output/df_study1_ind_comunas.html"))
```

>>>>

#Impute midpoint of income ranges
elsoc_long_2016_2021$m30_rec <-
as.numeric(car::recode(elsoc_long_2016_2021$m30,
           "1=110000;2=251000;3=305000;4=355000;5=400000;
            6=445000;7=490000;8=535000;9=585000;10=640000;11=700000;12=765000;
            13=845000;14=935000;15=1040000;16=1180000;17=1375000;18=1670000;
            19=2275000;20=2700000;NA=NA;c(-888,-999)=NA"))

#Impute midpoint of income ranges (2021)
elsoc_long_2016_2021$m30b_rec <-
as.numeric(car::recode(elsoc_long_2016_2021$m30b,
           "1=125000;2=300000;3=400000;4=575000;5=70000;NA=NA;c(-888,-999)=NA"))

sjmisc::frq(elsoc_long_2016_2021$m30b_rec)

#Recode DK/DA of Income to NA
elsoc_long_2016_2021$m29_rec <-
  as.numeric(car::recode(elsoc_long_2016_2021$m29,"c(-888,-999)=NA"))

#replace NA of income with new imputed variable
elsoc_long_2016_2021$m29_imp <- 
  ifelse(test = !is.na(elsoc_long_2016_2021$m29_rec),
         yes =  elsoc_long_2016_2021$m29_rec,
         no =  elsoc_long_2016_2021$m30_rec)
summary(elsoc_long_2016_2021$m29_imp)

elsoc_long_2016_2021$m29_imp <- 
  ifelse(test = is.na(elsoc_long_2016_2021$m29_imp),
         yes =  elsoc_long_2016_2021$m30b_rec,
         no =  elsoc_long_2016_2021$m29_imp)
summary(elsoc_long_2016_2021$m29_imp)

@@

# N Household:
elsoc_long_2016_2021 <-
  elsoc_long_2016_2021 %>%
  mutate(n_hogar =
           dplyr::case_when(ola == 1 ~ nhogar1,
                            ola == 2 ~ m46_nhogar,
                            ola == 3 ~ m54,
                            ola == 4 ~ m54,
                            ola == 5 ~ m54))
sjmisc::frq(elsoc_long_2016_2021$n_hogar)

@@

elsoc_long_2016_2021$quintil <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$quintil,
                      label = "Household income quintile per capita")

@@

elsoc_long_2016_2021$quintil1 <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$quintil1,
                      label = "Household income quintile per capita (NA)") 
sjmisc::frq(elsoc_long_2016_2021$quintil1)
#Age Ranges
elsoc_long_2016_2021$edad <- 
  factor(car::recode(elsoc_long_2016_2021$m0_edad, 
                     "18:29=1;30:49=2;50:64=3;65:150=4"),
         labels = c('18-29', '30-49', '50-64', '65 or more'))
elsoc_long_2016_2021$edad <-
  sjlabelled::set_label(elsoc_long_2016_2021$edad, 
                        label = c("Age groups")) 
# Other controls______________________________________________________________
# Subjective social status: individual ____________________________

@@

elsoc_long_2016_2021$know_inm <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$know_inm, 
                      label = "Known: Immigrants") 
elsoc_long_2016_2021$know_inm <-
sjlabelled::set_labels(x = elsoc_long_2016_2021$know_inm,
                       labels = c("None","Few","Some","Quite a few","Many"))
sjmisc::frq(elsoc_long_2016_2021$know_inm)

# Level of contact: Migrant friends_________________________
sjmisc::frq(elsoc_long_2016_2021$r05_02)
elsoc_long_2016_2021$frien_inm <- 
elsoc_long_2016_2021$r05_02

elsoc_long_2016_2021$frien_inm <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$frien_inm, 
                      label = "Level of contact: Inmigrant friends")

elsoc_long_2016_2021$frien_inm <-
sjlabelled::set_labels(x = elsoc_long_2016_2021$frien_inm,
                       labels = c("None","Few","Some","Quite a few","Many"))
sjmisc::frq(elsoc_long_2016_2021$frien_inm)

@@

# CONTACT_______________________________________________________________

# NATION to wave 1 (original)___________________
df_nation <- elsoc_long_2016_2021 %>%  
  select(idencuesta,nation_fix=nation,ola,muestra) %>% 
  filter(ola %in% c(1,3)) %>% #keep wave 1 and 3 
  group_by(idencuesta) %>% 
  summarise(nation_fix=max(nation_fix,na.rm = F)) #keep the maximum value 
sjmisc::frq(df_nation$nation_fix) # 2 NA

elsoc <- elsoc_long_2016_2021 #dummy dataset _________________________________

# merge the data with fixed variable:
elsoc <- left_join(x = elsoc,y = df_nation,by ="idencuesta") 
# sjmisc::frq(elsoc$nation_fix)

table(elsoc$nation==elsoc$nation_fix) #how many cases are different ?
elsoc$check_nation <- ifelse(elsoc$nation==elsoc$nation_fix,
                             yes = "IGUALES",
                             no = "DISTINTOS")
# sjmisc::frq(elsoc$check_nation) #18 cases

# edit, if value is different from original variable, set the value of wave 1
elsoc$nation_t1 <- if_else(condition = elsoc$check_nation=="DISTINTOS",
                           true = elsoc$nation,
                           false = elsoc$nation_fix,
                           missing = elsoc$nation_fix)

table(elsoc$nation==elsoc$nation_t1)
sjmisc::frq(elsoc$nation_t1)
elsoc$nation <- NULL; elsoc$nation_fix <- NULL; elsoc$check_nation <- NULL

elsoc$nation_t1 <- set_label(elsoc$nation_t1, label = "Nationality")

# KNOW inmigrants _____________________________
sjPlot::tab_xtab(elsoc$know_inm,
                 elsoc$ola,show.cell.prc = T,show.na = T)
sjmisc::frq(elsoc$know_inm)
elsoc$know_inm_bi <- car::recode(elsoc$know_inm,
                                                "1=0;2:5=1")
sjmisc::frq(elsoc$know_inm_bi)

know_inm_bi <- 
elsoc %>% group_by(idencuesta) %>%
  summarize(
            know_inm_t1t4 = know_inm_bi[ola==4] - know_inm_bi[ola==1]
            )

elsoc <- left_join(x = elsoc,y = know_inm_bi, by = "idencuesta")
elsoc$know_inm_t1t4 <- set_label(elsoc$know_inm_t1t4,
                                  label = "Know immigrants (diff. t4 - t1)")
# sjmisc::frq(elsoc$know_inm_t1t4)
# sjPlot::tab_xtab(elsoc$know_inm_t1t4,elsoc$ola)

# FRIENDS inmigrants _____________________________
sjPlot::tab_xtab(elsoc$frien_inm,
                 elsoc$ola,show.cell.prc = T,show.na = T)
sjmisc::frq(elsoc$frien_inm)
elsoc$frien_inm_bi <- car::recode(elsoc$frien_inm,
                                                "1=0;2:5=1")
sjmisc::frq(elsoc$frien_inm_bi)

frien_inm_bi <- 
elsoc %>% group_by(idencuesta) %>%
  summarize(
            frien_inm_t1t4 = frien_inm_bi[ola==4] - frien_inm_bi[ola==1]
            )

elsoc <- left_join(x = elsoc,y = frien_inm_bi, by = "idencuesta")

elsoc$frien_inm_t1t4 <- set_label(elsoc$frien_inm_t1t4,
                                  label = "Have immigrant friends (diff. t4 - t1)")
# sjmisc::frq(elsoc$frien_inm_bi)
# sjmisc::frq(elsoc$frien_inm_t1t4)
# sjPlot::tab_xtab(elsoc$frien_inm_t1t4,elsoc$ola)

# Select variables______________________________________________________________
elsoc_long_2016_2021<- elsoc

df_study1 <- 
elsoc_long_2016_2021 %>% 
  select(idencuesta,ola,region,region_cod,comuna,comuna_cod,
         muestra,
         cuestion_mig,
         starts_with("in_"),
         educ,educ_n,ing_pc,quintil,quintil1,
         ess,
         # ess_inm,
         nation_t1,
         know_inm,
         know_inm_bi,
         know_inm_t1t4,
         frien_inm,
         frien_inm_bi,
         frien_inm_t1t4,
         pos_id,
         edad)  %>% 
  filter(muestra == 1) #keep original sample (vs refresh)

# sjmisc::frq(df_study1$ola)
sjPlot::tab_xtab(df_study1$muestra,df_study1$ola)

df_study1_2 <- 
elsoc_long_2016_2021 %>% 
  select(idencuesta,ola,region,region_cod,comuna,comuna_cod,
         muestra,
         cuestion_mig,
         starts_with("in_"),
         educ,
         educ_n,
         ing_pc,
         quintil,
         quintil1,
         ess,
         nation_t1,
         know_inm_t1t4,
         frien_inm_t1t4,
         pos_id,
         edad
         ) %>% 
  filter(muestra == 1) %>% #keep original sample (vs refresh)
  na.omit()

sjPlot::view_df(df_study1_2,show.frq = T,show.values = T,show.na = T,show.prc = T)
sjPlot::tab_xtab(var.row = df_study1_2$muestra,
                 var.col = df_study1_2$ola)

# sjmisc::frq(df_study1_2$ola)
# sjmisc::frq(df_study1_2$muestra)
# sjmisc::frq(df_study1_2$cuestion_mig)
# sjmisc::frq(df_study1_2$idencuesta,show.na = F) %>% data.frame() %>% View()

# Dataset fixed at t5_________________________________________________________
# keep idencuesta for the t5
id <- distinct(df_study1_2 %>% select(idencuesta,ola) %>% filter(ola==5))
# filter data by the idencuesta of t5
df_study1_3 <- 
  df_study1_2 %>%  filter(idencuesta %in% id$idencuesta)

# sjmisc::frq(df_study1_2$comuna)
# sjPlot::view_df(df_study1_3,show.frq = T,show.values = T,show.na = T,show.prc = T)
# 
# sjPlot::tab_xtab(var.row = df_study1_3$cuestion_mig,
#                  var.col = df_study1_3$ola)
# 
# sjPlot::tab_xtab(var.row = df_study1_3$muestra,
#                  var.col = df_study1_3$ola)

@@

# SAVE DATA____________________________________________________________________
save(df_study1,file = here::here("input/data-proc/study_1.RData"))
save(df_study1_2,file = here::here("input/data-proc/study_1_2.RData"))
save(df_study1_3,file = here::here("input/data-proc/study_1_3.RData"))

# # save codebook
sjPlot::view_df(df_study1,
        show.frq = T,
        show.prc = T,
        show.na = T,
        file = here::here("output/df_study1.html"))

sjPlot::view_df(df_study1_2,
        show.frq = T,
        show.prc = T,
        show.na = T,
        file = here::here("output/df_study1_2.html"))

sjPlot::view_df(df_study1_3,
        show.frq = T,
        show.prc = T,
        show.na = T,
        file = here::here("output/df_study1_3.html"))
```

@@

load(file = here::here("input/data-proc/study_1.RData"))
load(file = here::here("input/data-proc/study_1_2.RData"))
load(file = here::here("input/data-proc/study_1_3.RData"))
load(file = here::here("input/data-proc/study_1_comunas.RData"))

@@

df_study1_2_ind_comunas <- 
 dplyr::left_join(x = df_study1_2,
                  y = df_study1_comunas, 
                  by = "comuna_cod") %>% 
 dplyr::select(idencuesta:edad,
               inm_prop_cas17_w,
               inm_prop_cas20_w,
               dif_inm) %>% 
 dplyr::rename(comuna=comuna.x)

df_study1_3_ind_comunas <- 
 dplyr::left_join(x = df_study1_3,
                  y = df_study1_comunas, 
                  by = "comuna_cod") %>% 
 dplyr::select(idencuesta:edad,
               inm_prop_cas17_w,
               inm_prop_cas20_w,
               dif_inm) %>% 
 dplyr::rename(comuna=comuna.x)

# save data____________________________________________________________________
save(df_study1_ind_comunas,
     file = here::here("input/data-proc/df_study1_ind_comunas.RData"))
save(df_study1_2_ind_comunas,
     file = here::here("input/data-proc/df_study1_2_ind_comunas.RData"))
save(df_study1_3_ind_comunas,
     file = here::here("input/data-proc/df_study1_3_ind_comunas.RData"))

# save codebook
sjPlot::view_df(df_study1_ind_comunas,
        show.frq = T, 
        show.prc = T, 
        show.na = T,
        file = here::here("output/df_study1_ind_comunas.html"))

sjPlot::view_df(df_study1_2_ind_comunas,
        show.frq = T, 
        show.prc = T, 
        show.na = T,
        file = here::here("output/df_study1_2_ind_comunas.html"))

sjPlot::view_df(df_study1_3_ind_comunas,
        show.frq = T, 
        show.prc = T, 
        show.na = T,
        file = here::here("output/df_study1_3_ind_comunas.html"))
```
